What makes listeners infer teaching intentions?

### 2022-02-01 paper/manuscript.Rmd
update abstract
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

abstract: |
  Social learning plays an important role in human skill transmission. It has been known that experts tend to change their behaviour particularly for teaching purposes. Our previous research demonstrated that expert pianists systematically modulated their sound so as to teach musical expressive techniques such as articulation and dynamics. For example, pianists played slower and exaggerated each technique when they had an intention to teach. In order to achieve successful skill transmission, it is vital to examine whether such sound modulations are identified and used to infer teaching intentions by novices, who are going to acquire skills. The current experiments investigated which features of piano performance make musicians (in the role of potential learners) infer teaching intentions. Musicians listened to a number of piano recordings where a musical expressive technique of either articulation or dynamics was implemented. Musicians were asked to judge whether each performance was produced in order to teach the designated expressive technique. We quantified recordings with regard to tempo, articulation and dynamics. Overall, slower tempo contributed to musicians’ judgments as teaching. Moreover, performances with exaggeration for each technique (e.g., shorter staccato, larger contrast between forte and piano) were more likely to be judged as teaching. These performance features are consistent with expert pianists’ sound modulations for teaching purposes. Therefore, musicians (in the role of potential learners) seem to be able to identify didactic sound modulations, only by listening to recorded performances.

@@

Tominaga, Knoblich & Sebanz (*in prep*) extended this line of research to expertise transmission where skills to be acquired are much more complicated than general knowledge, which is mostly acquired throughout development [e.g., @csibra_2009]. Expertise usually demands an enormous amount of practice to acquire so that only experts can accomplish a higher level of performance including artistic expression. Based on the assumption that expert pianists are very good at controlling and modulating their sound to communicate, we investigated how expert pianists could modulate their performance when they were intending to teach musical expressive techniques of articulation (the smoothness of sound) and dynamics (the loudness of sound). The results demonstrated that expert pianists could successfully modulate their performance by playing slower or exaggerating relevant aspects of the performance (e.g., producing shorter staccato or making a larger contrast between forte and piano) to teach musical expressive techniques. Therefore, it seems that even in the domain of expertise, experts exhibit general pedagogical behaviours to communicate with their potential learners.

>>>>

abstract: |
  Social learning plays an important role in human skill transmission. It has been known that experts tend to change their behaviour particularly for teaching purposes. Our previous research demonstrated that expert pianists systematically modulated their sound so as to teach musical expressive techniques such as articulation and dynamics. For example, pianists played slower and exaggerated each technique when they had an intention to teach. Here we investigated whether the modulations that expert pianists produce when they intend to teach are also perceived by listeners as conveying pedagogical intentions. In the current study, musicians listened to piano recordings where a musical expressive technique of either articulation or dynamics was implemented. They were asked to judge whether each performance was produced to teach the designated expressive technique or not. We quantified recordings with regard to tempo, articulation and dynamics. We performed correlation and regression analysis to investigate which features of piano performance make musicians infer teaching intention. The findings in Experiment 1 with a simple musical scales demonstrated that slower tempo contributed to musicians’ judgments as teaching regardless of the techniques. Moreover, performances with exaggeration for each technique (e.g., longer legato, shorter staccato, larger contrast between forte and piano) were more likely to be judged as teaching. We run Experiment 2 with a more naturalistic piece to replicate the findings of Experiment 1. We only replicated the findings related to dynamics (e.g., larger contrast between forte and piano). Taken together, dynamics features of piano performance were more reliably perceived by musicians to infer pedagogical intentions.

@@

Tominaga, Knoblich & Sebanz (*submitted*) extended this line of research to expertise transmission where skills to be acquired are much more complicated than general knowledge, which is mostly acquired throughout development [e.g., @csibra_2009]. Expertise usually demands an enormous amount of practice to acquire so that only experts can accomplish a higher level of performance including artistic expression. Based on the assumption that expert pianists are very good at controlling and modulating their sound to communicate, we investigated how expert pianists could modulate their performance when they were intending to teach musical expressive techniques of articulation (the smoothness of sound) and dynamics (the loudness of sound). The results demonstrated that expert pianists could successfully modulate their performance by playing slower or exaggerating relevant aspects of the performance (e.g., producing shorter staccato or making a larger contrast between forte and piano) to teach musical expressive techniques. Therefore, it seems that even in the domain of expertise, experts exhibit general pedagogical behaviours to communicate with their potential learners.

### 2022-02-01 paper/manuscript.tex
update abstract
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

\abstract{
Social learning plays an important role in human skill transmission. It has been known that experts tend to change their behaviour particularly for teaching purposes. Our previous research demonstrated that expert pianists systematically modulated their sound so as to teach musical expressive techniques such as articulation and dynamics. For example, pianists played slower and exaggerated each technique when they had an intention to teach. In order to achieve successful skill transmission, it is vital to examine whether such sound modulations are identified and used to infer teaching intentions by novices, who are going to acquire skills. The current experiments investigated which features of piano performance make musicians (in the role of potential learners) infer teaching intentions. Musicians listened to a number of piano recordings where a musical expressive technique of either articulation or dynamics was implemented. Musicians were asked to judge whether each performance was produced in order to teach the designated expressive technique. We quantified recordings with regard to tempo, articulation and dynamics. Overall, slower tempo contributed to musicians' judgments as teaching. Moreover, performances with exaggeration for each technique (e.g., shorter staccato, larger contrast between forte and piano) were more likely to be judged as teaching. These performance features are consistent with expert pianists' sound modulations for teaching purposes. Therefore, musicians (in the role of potential learners) seem to be able to identify didactic sound modulations, only by listening to recorded performances.
}

@@

Tominaga, Knoblich \& Sebanz (\emph{in prep}) extended this line of research to expertise transmission where skills to be acquired are much more complicated than general knowledge, which is mostly acquired throughout development (e.g., Csibra \& Gergely, 2009). Expertise usually demands an enormous amount of practice to acquire so that only experts can accomplish a higher level of performance including artistic expression. Based on the assumption that expert pianists are very good at controlling and modulating their sound to communicate, we investigated how expert pianists could modulate their performance when they were intending to teach musical expressive techniques of articulation (the smoothness of sound) and dynamics (the loudness of sound). The results demonstrated that expert pianists could successfully modulate their performance by playing slower or exaggerating relevant aspects of the performance (e.g., producing shorter staccato or making a larger contrast between forte and piano) to teach musical expressive techniques. Therefore, it seems that even in the domain of expertise, experts exhibit general pedagogical behaviours to communicate with their potential learners.

>>>>

\abstract{
Social learning plays an important role in human skill transmission. It has been known that experts tend to change their behaviour particularly for teaching purposes. Our previous research demonstrated that expert pianists systematically modulated their sound so as to teach musical expressive techniques such as articulation and dynamics. For example, pianists played slower and exaggerated each technique when they had an intention to teach. Here we investigated whether the modulations that expert pianists produce when they intend to teach are also perceived by listeners as conveying pedagogical intentions. In the current study, musicians listened to piano recordings where a musical expressive technique of either articulation or dynamics was implemented. They were asked to judge whether each performance was produced to teach the designated expressive technique or not. We quantified recordings with regard to tempo, articulation and dynamics. We performed correlation and regression analysis to investigate which features of piano performance make musicians infer teaching intention. The findings in Experiment 1 with a simple musical scales demonstrated that slower tempo contributed to musicians' judgments as teaching regardless of the techniques. Moreover, performances with exaggeration for each technique (e.g., longer legato, shorter staccato, larger contrast between forte and piano) were more likely to be judged as teaching. We run Experiment 2 with a more naturalistic piece to replicate the findings of Experiment 1. We only replicated the findings related to dynamics (e.g., larger contrast between forte and piano). Taken together, dynamics features of piano performance were more reliably perceived by musicians to infer pedagogical intentions.
}

@@

Tominaga, Knoblich \& Sebanz (\emph{submitted}) extended this line of research to expertise transmission where skills to be acquired are much more complicated than general knowledge, which is mostly acquired throughout development (e.g., Csibra \& Gergely, 2009). Expertise usually demands an enormous amount of practice to acquire so that only experts can accomplish a higher level of performance including artistic expression. Based on the assumption that expert pianists are very good at controlling and modulating their sound to communicate, we investigated how expert pianists could modulate their performance when they were intending to teach musical expressive techniques of articulation (the smoothness of sound) and dynamics (the loudness of sound). The results demonstrated that expert pianists could successfully modulate their performance by playing slower or exaggerating relevant aspects of the performance (e.g., producing shorter staccato or making a larger contrast between forte and piano) to teach musical expressive techniques. Therefore, it seems that even in the domain of expertise, experts exhibit general pedagogical behaviours to communicate with their potential learners.
